D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-18 ootavacuous.tex
Jade Alglave March 18 feedback
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Figure~\ref{fig:On x86, rfe Links Are Temporal}
plots a histogram of the elapsed time from the store of a new value
to the first load of that new value.
Here all of the data falls into positive time, indicating
that rfe links always go forward in global time, as those familiar with
computer hardware and the laws of physics would expect.

>>>>

Figure~\ref{fig:On x86, rfe Links Are Temporal}
plots a histogram of the elapsed time from the store of a new value
to the first load of that new value.
Here all of the data falls into positive time, indicating
that rfe links always go forward in global time, as those familiar with
computer hardware, limits on speculative execution, and the laws of
physics would expect.\footnote{
	Our apologies to those who might feel that this is belaboring
	the obvious.
	And please understand that these points have proven helpful to
	some of those whose whose work has never strayed too close to
	hardware.}
